### 2014-11-13 tex/intro.tex

In recent years symbolic execution has provided the basis for various
software testing and analysis techniques. Symbolic execution
systematically explores the program execution space using symbolic
input values, and for each explored path, computes constraints on the
symbolic inputs to create a \emph{ path condition}.  The path
conditions computed by symbolic execution characterize the observed
program execution behaviours and have been used as an enabling
technology for various applications, e.g., regression
analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
data structure repair~\cite{KhurshidETAL05RepairingStructurally},
dynamic discovery of
invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
debugging~\cite{Ma:2011}.

Initial work on symbolic execution largely focused on checking
properties of programs with primitive
types~\cite{clarke76TSE,King:76}.  With the advent of object-oriented
languages, recent work has generalized the core ideas of symbolic
execution to enable analysis of programs containing complex data
structures with unbounded domains, i.e., data stored on the
heap~\cite{Kiasan06,Kiasan07,GSE03}.  These \emph{Generalized Symbolic
  Execution} (GSE) techniques construct the heap in a lazy manner,
deferring materialization of objects on the concrete heap until they
are needed for the analysis to proceed. The materilization creates
additional non-deterministic choice points in the symbolic execution
tree by representing the feasible heap configurations as (i) null,
(ii) an instance of a new reference of a compatible class, and (iii)
an alias to a previously initialized symbolic reference.  Symbolic
execution then follows concrete program semantics for materialized
heap locations. Although this approach enables the analysis of heap
manipulating programs, a large number of feasible concrete heap
configurations are created leading to a path explosion.

>>>>

In recent years symbolic execution has provided the basis for various
software testing and analysis techniques. Symbolic execution
systematically explores the program execution space using symbolic
input values, and for each explored path, computes constraints on the
symbolic inputs to create a \emph{ path condition}.  The path
conditions computed by symbolic execution characterize the observed
program execution behaviors and have been used as an enabling
technology for various applications, e.g., regression
analysis~\cite{backes:2012,Godefroid:SAS11,Person:FSE08,person:pldi2011,Ramos:2011,Yang:ISSTA12},
data structure repair~\cite{KhurshidETAL05RepairingStructurally},
dynamic discovery of
invariants~\cite{CsallnerETAL08DySy,Zhang:ISSTA14}, and
debugging~\cite{Ma:2011}.

Initial work on symbolic execution largely focused on checking
properties of programs with primitive
types~\cite{clarke76TSE,King:76}.  With the advent of object-oriented
languages, recent work has generalized the core ideas of symbolic
execution to enable analysis of programs containing complex data
structures with unbounded domains, i.e., data stored on the
heap~\cite{Kiasan06,Kiasan07,GSE03}.  These \emph{Generalized Symbolic
  Execution} (GSE) techniques construct the heap in a lazy manner,
deferring materialization of objects on the concrete heap until they
are needed for the analysis to proceed. The materialization creates
additional non-deterministic choice points in the symbolic execution
tree by representing the feasible heap configurations as (i) null,
(ii) an instance of a new reference of a compatible class, and (iii)
an alias to a previously initialized symbolic reference.  Symbolic
execution then follows concrete program semantics for materialized
heap locations. Although this approach enables the analysis of heap
manipulating programs, a large number of feasible concrete heap
configurations are created leading to a path explosion.
